Universal Anonymous Signatures

### 2022-02-28 prism-backend/research/gsac/model-uas.tex
Creating a separate document for UAS.

\textcolor{red}{\textbf{WARNING:} The syntax and oracles below should be close
  to what we want. The game definitions should may be farther (especially
  traceability and non-frameability), but I'm having trouble with this level
  of abstraction without having some concrete scheme to consult on. Therefore,
  I'll start with a generic construction and then iterate the model again.
  Thus, note that the current modelling is, essentially, wrong.}

Universal Anonymous Signatures.

@@

\subsection{Functionality ``Transformations''}
\label{ssec:transformations}

@@

\todo{I think this might be possible if we can use \fissue so that any user can
  create arbitrary groups, where he is the issuer, an can thus run
  \Obtain,\Issue protocols to combine credentials from other groups. This is
  probably inefficient (or, at least, more than doing so wihtout having to
  creat ad hoc groups), but at least allows the enhanced functionality...}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "gsac"
%%% End:

>>>>

@@

\subsection{Functionality ``Transformations'' and Special Cases}
\label{ssec:transformations}

@@

\todo{I think this might be possible if we can use \fissue so that any user can
  create arbitrary groups, where he is the issuer, an can thus run
  \Obtain,\Issue protocols to combine credentials from other groups. This is
  probably inefficient (or, at least, more than doing so wihtout having to
  create ad hoc groups), but at least allows the enhanced functionality...}

\subsubsection{Restricting to Conventional GS and AC Schemes}

\subsubsection{Group Signatures with Message Dependent Opening}

\todo{Describe what type of \finsp would be needed to achieve a functionality
  similar to that of GS-MDO. Does this fit our model straight away? Maybe also
  show how other types of GS could be ``mimicked'' (e.g., GS only with linking).
  This would also be good to test if the model is as generic as I think it is}

\subsubsection{Ring Signatures}

\todo{Can we leverage the \fissue and/or \feval predicates to make our model
  suitable for some sort of Ring Signature scheme?}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:
